``Vendetta'': End-to-end auditable voting

### 2012-11-15 proposal/proposal.tex
First draft of the proposal
Added a first draft that certainly warrants additional work. Little
research has been performed (on my part) at this point, so it's more of
a "statement of objectives" -- nearly what we discussed in-person.

So, I think the next step is research. Can we clarify the goals we
believe a system should meet? We also need to find "real" references
(not Wikipedia). Finally, we need to clarify what we're going to do, as
I don't think I accurately captured it in what I have written at
present.

	\todo{Write the proposal.}
	\cite{dummy}

>>>>

	\section{Background}

		A democratic voting system like that in the United States raises several questions to which
		cryptography can potentially provide answers. Namely, the question at hand is \emph{how to keep
		voting fair}. In particular, we want to consider the following questions:
		\begin{itemize}

			\item
				How can a government prove to a voter that his/her vote \emph{was} counted (correctly),
				without being able to reveal the candidate for which the ballot was cast?

			\item
				How can an observer verify that the votes reported by a state contain no forged votes (i.e.,
				that the state is not cheating by introducing votes not actually cast)?

		\end{itemize}
		Cryptographic systems designed to meet exactly these goals are called \term{end-to-end auditable
		voting systems}\cite{end_to_end}.

		A wealth of research has been done in this area, and a number of such systems have been devised.
		Most of these systems have been developed by academia. However, countries such as Estonia and
		even the United States have developed systems for voting via the Internet
		\cite{estonia,us_vs_est} -- and while that is only tangential to the questions posed above, it
		can be instructive to see how (if at all) these systems meet those goals.

	\section{Proposal}

		We plan to begin with a more precise quantification of the security goals that we believe must
		be met for a voting system (whether physical or digital) in order to accomplish the higher-level
		goals questioned above. We will then survey existing research on such cryptographic systems to
		determine whether any fully meet the security requirements.

		Should an existing system sufficiently meet our requirements, we plan to construct a
		proof-of-concept implementation of the system along with an analysis both of its effectiveness
		at ensuring fairness and of the feasibility of employing such a system in the real world.

		Otherwise, we will examine the flaws and strengths of the existing designs and attempt to
		construct a sufficient system -- or in the least, one that shows a marked improvement over
		prior work. We will then provide an analysis of how our proposed \emph{new} system meets the
		stated goals and could prove useful in a real-world deployment. Time permitting, we will also
		implement a proof-of-concept for our scheme.
